The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Update code chunk lables, options, names and todos

```{r setup}
#| echo: false
#| warning: false

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph"                            # Network analysis and visualization
)

@@

## Read only metadata for theses with PDF available
emu <- read_csv(here(data_path, "theses-metadata.csv")) |>
  mutate(text = "") |>
  filter(!is.na(pdf_via))

@@

```{r get-pdf-text}
#| echo: false
#| cache: true

@@

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu$text <- convert_pdf_text(pdf_paths)

@@

  # Write thesis dataframe to file
  write_csv(emu, data_path)
} else {
  emu$text <- read_csv(data_path)$text
  emu$longitude <- read_csv(data_path)$longitude
  emu$latitude <- read_csv(data_path)$latitude
}

@@

```{r topic-model-lda}
#| dependson: short-stop-words

@@

```{r topic-model-lda}

@@

```{r topic-model-beta}
#| dependson: topic-model-lda

>>>>

```{r setup}
#| echo: false
#| warning: false
#| message: false

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  # TODO remove reshape2 if `melt()` is replaced by`pivot_longer()`
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph"                            # Network analysis and visualization
)

@@

## Read only metadata for theses with PDF available
emu <- read_csv(here(data_path, "theses-metadata.csv")) |>
  mutate(text_raw = "") |>
  filter(!is.na(pdf_via))

@@

```{r get-pdf-text}
#| echo: false
#| cache: true
#| message: false

@@

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu$text_raw <- convert_pdf_text(pdf_paths)

@@

  # Write thesis dataframe to file
  write_csv(emu, data_path)
} else {
  emu$text_raw <- read_csv(data_path)$text
  emu$longitude <- read_csv(data_path)$longitude
  emu$latitude <- read_csv(data_path)$latitude
}

@@

```{r topic-model-lda-1}
#| dependson: short-stop-words

@@

```{r topic-model-lda-2}

@@

```{r topic-model-beta}
